Survey of Misuses of the Kolmogorov–Smirnov-Test

### 2022-02-25 Manuscript/manuscript.tex
updated manuscript pdfs and citations

\begin{figure}[!ht]
  \centering
  \includegraphics[scale=0.7]{hist_parametric}
  \caption{Histograms demonstrating fitted parameters.}
  \label{fig:hist_parametric}
\end{figure}

@@

\begin{figure}[!ht]
  \centering
  \includegraphics[scale=0.7]{hist_rounded}
  \caption{Histograms of P-values with rounded data.}
  \label{fig:hist_rounded}
\end{figure}

@@

In addition, a proposed revision of the K-S test can be found in \citet{dgof}.\citet{dgof} provides a revision to R's `ks-test()` function for the case that the null distribution is discrete.

\begin{figure}[!ht]
  \centering
  \includegraphics[scale=0.7]{hist_dgof}
  \caption{Histograms of P-values with dgof package.}
  \label{fig:hist_dgof}
\end{figure}

\begin{figure}[!ht]
  \centering
  \includegraphics[scale=0.7]{hist_dgofsim}
  \caption{Histograms of P-values when simulating p-value.}
  \label{fig:hist_dgofsim}
\end{figure}

@@

\begin{figure}[!ht]
  \centering
  \includegraphics[scale=0.7]{hist_correlation}
  \caption{Histograms of P-values with correlated data.}
  \label{fig:hist_correlation}
\end{figure}

@@

\citet{Steinskog}
\citet{Weiss}
\citet{Massey}
\citet{Lilliefors}
\citet{dgof}
\citet{Conover}
\citet{Gleser}

>>>>

\begin{figure}[tbp]
  \centering
  \includegraphics{hist_parametric}
  \caption{Histograms demonstrating fitted parameters.}
  \label{fig:hist_parametric}
\end{figure}

@@

\begin{figure}[tbp]
  \centering
  \includegraphics{hist_rounded}
  \caption{Histograms of P-values with rounded data.}
  \label{fig:hist_rounded}
\end{figure}

@@

In addition, a proposed revision of the K-S test can be found in \citet{dgof}.\citet{dgof} provides a revision to R's `ks.test()` function for the case that the null distribution is discrete.

\begin{figure}[tbp]
  \centering
  \includegraphics{hist_general}
  \caption{Histograms of P-values with KSGeneral and dgof packages.}
  \label{fig:hist_general}
\end{figure}

@@

\begin{figure}[tbp]
  \centering
  \includegraphics{hist_correlation}
  \caption{Histograms of P-values with correlated data.}
  \label{fig:hist_correlation}
\end{figure}

\begin{figure}[tbp]
  \centering
  \includegraphics{hist_block}
  \caption{Histograms of P-values when using block bootstrap.}
  \label{fig:hist_block}
\end{figure}

@@

\citet{Steinskog}
\citet{Weiss}
\citet{Massey}
\citet{Lilliefors}
\citet{Arnold}
\citet{Conover}
\citet{Gleser}
\citet{Babu}
\citet{Butorina}
\citet{Racine}
\citet{Wang}
\citet{Capasso}
\citet{Dimitrova}
